Kids PM Summary

### 2020-05-22 manuscript_tables_figures.Rmd
exposure analysis/model updates

---
title: 'KidsAIR: manuscript tables/figures'
author: "Ethan Walker"
date: "Started 13 May 2020, Updated 14 May 2020"
output:
  powerpoint_presentation: default
---

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(total_n = n()) %>% 
  group_by(area) %>% 
  mutate(area_n = n()) %>% 
  group_by(new_var) %>% 
  mutate(n = n(),
         percent = n()/total_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  select(new_var, n, percent)
demographics_summary
}

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(total_n = n()) %>% 
  group_by(area) %>% 
  mutate(area_n = n()) %>% 
  group_by(area, new_var) %>% 
  mutate(n = n(),
         percent = n()/area_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  select(new_var, n, percent) %>% 
  arrange(area, new_var)
demographics_summary
}

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  select(area, home, new_var) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  select(area, home, new_var) %>% 
  group_by(area) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

@@

```{r}
other_vars_total <- exposure_analysis_data_short %>% 
  rename(new_var = home_act_sweep_sum) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  select(area, home, new_var) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
other_vars_total

other_vars_area <- exposure_analysis_data_short %>% 
  rename(new_var = home_act_sweep_sum) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  select(area, home, new_var) %>% 
  group_by(area) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
other_vars_area
```

>>>>

---
title: 'KidsAIR: manuscript tables/figures'
author: "Ethan Walker"
date: "Started 13 May 2020, Updated 22 May 2020"
output:
  powerpoint_presentation: default
---

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>%
  filter(home != "WMA300") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(total_n = n()) %>% 
  group_by(area) %>% 
  mutate(area_n = n()) %>% 
  group_by(new_var) %>% 
  mutate(n = n(),
         percent = n()/total_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  select(new_var, n, percent)
demographics_summary
}

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  filter(home != "WMA300") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(total_n = n()) %>% 
  group_by(area) %>% 
  mutate(area_n = n()) %>% 
  group_by(area, new_var) %>% 
  mutate(n = n(),
         percent = n()/area_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  select(new_var, n, percent) %>% 
  arrange(area, new_var)
demographics_summary
}

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  filter(home != "WMA300") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  select(area, home, new_var) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>%
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>%
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  filter(home != "WMA300") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  select(area, home, new_var) %>% 
  group_by(area) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

@@

```{r}
other_vars_total <- exposure_analysis_data_short %>% 
  rename(new_var = sums_events_sampling_period) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  filter(home != "WMA300") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  select(area, home, new_var) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
other_vars_total

other_vars_area <- exposure_analysis_data_short %>% 
  rename(new_var = sums_events_sampling_period) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  filter(home != "WMA300") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  select(area, home, new_var) %>% 
  group_by(area) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
other_vars_area
```

### 2020-05-22 pm_summary.Rmd
exposure analysis/model updates

```{r}
# home that exceed PM guidelines
pm_guidelines <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(pm_mean_sampling_period > 35) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  group_by(area) %>% 
  count()
pm_guidelines
```

>>>>

```{r}
# homes that exceed PM guidelines
pm_guidelines <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(home != "WMA300") %>% 
  filter(pm_mean_sampling_period > 35) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  group_by(area) %>% 
  count()
pm_guidelines

#Pm by different levels of covariates
pm_check <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(home != "WMA300") %>% 
  distinct(home, .keep_all = TRUE) %>% 
  group_by(chimney_clean_3level) %>% 
  summarize("n" = n(),
            "Mean PM" = round(mean(pm_mean_sampling_period, na.rm = TRUE)), 
            "SD PM" = round(sd(pm_mean_sampling_period, na.rm = TRUE)),
            "Min PM" = round(min(pm_mean_sampling_period, na.rm = TRUE)), 
            "25%" = round(quantile(pm_mean_sampling_period, 0.25, na.rm = TRUE)),
            "Median PM" = round(median(pm_mean_sampling_period, na.rm = TRUE)),
            "75%" = round(quantile(pm_mean_sampling_period, 0.75, na.rm = TRUE)),
            "Max PM" = round(max(pm_mean_sampling_period, na.rm = TRUE)))
pm_check

# closer look at stove grade and PM
pm_stove_grade <- exposure_analysis_data_short %>%
  select(area, home, pm_mean_sampling_period, stove_grade_3level, 
         treatment, winter_id, home_winter_id) %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(home != "WMA300") %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(stove_grade_2level = fct_collapse(stove_grade_3level,
                                           "A" = "A",
                                           "C or F" = c("C", "F"))) %>% 
  group_by(stove_grade_2level) %>% 
  summarize("n" = n(),
            "Mean PM" = round(mean(pm_mean_sampling_period, na.rm = TRUE)), 
            "SD PM" = round(sd(pm_mean_sampling_period, na.rm = TRUE)),
            "Min PM" = round(min(pm_mean_sampling_period, na.rm = TRUE)), 
            "25%" = round(quantile(pm_mean_sampling_period, 0.25, na.rm = TRUE)),
            "Median PM" = round(median(pm_mean_sampling_period, na.rm = TRUE)),
            "75%" = round(quantile(pm_mean_sampling_period, 0.75, na.rm = TRUE)),
            "Max PM" = round(max(pm_mean_sampling_period, na.rm = TRUE)))
pm_stove_grade

model_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(area == "WMT") %>% 
  filter(home != "WMA300") %>% 
  distinct(home, .keep_all = TRUE)

check_model <- lm(log(pm_mean_sampling_period) ~ stove_grade_3level,
                  data = model_data)

summary(check_model)
```
